### 2022-10-04 Proposal/Proposal.tex
commit #setupproposal

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{float}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{lipsum}
\title{My Statistics 3494W Proposal}

\author{Michael  Marcaccio}

\date{October 4 2022}

\begin{document}

\end{document}

### 2022-10-04 Proposal/Proposal.tex
commit #setup
commit #firstcite
commit #Introduction

@@
 \usepackage{lipsum}
+\usepackage[english]{babel}
+\usepackage[autostyle, english = american]{csquotes}
+\MakeOuterQuote{"}
 \title{My Statistics 3494W Proposal}
@@
 
+\maketitle
+
+\section*{Introduction}
+Call centers are a staple of the finanical industry with agents working in the United States, Europe, Asia and Africa \citep{ibrahim2016modeling}. 
+Effective management is essential to running call centers and businesses are consistently trying to model and optimize when customers are calling with questions. 
+\citet*{evensen1999effective} describes the recent growth of call centers as being, "viewed as little more than lower cost channels for customer
+problem resolution, are quickly becoming a powerful means of service delivery with a potential for substantial revenue generation".
+I have chosen this to be my topic of study as I have a strong interest in working in the finanical industry after graduation and I have an unique opportunity to utilize real-world data from an undisclosed
+finanical firm. Due to this, My findings may provide insight that would benefit the company and its members.
+
+\section*{Specific Aims}
+I will be attempting to model call volume per a 15 minute interval and determining if there is any seasonality in the calls.
+
+\bibliographystyle{chicago}
+\bibliography{citations.bib}
 \end{document}

### 2022-10-05 Proposal/Proposal.tex
commit #specificaims

@@
 \section*{Specific Aims}
-I will be attempting to model call volume per a 15 minute interval and determining if there is any seasonality in the calls.
+I will be attempting to model call volume per a 15 minute interval and determining if there is any seasonality in the calls. With each interval,
+I will find the optimal number of employees needed to handle the amount of incoming calls based on typical call length. This is extremely important
+to be able to forecast call volume and be optimally prepared with a proper number of employees for anticipated spikes in calls. If a business is not prepared
+this will create a increase in holdtime which will result in members becoming frustrated and discouraged.
+\citet*{ibrahim2016modeling} states, "The accurate modeling and forecasting of future call arrival volumes is a
+complicated issue which is critical for making important operational decisions, such as staffing and scheduling, in the call center".
 

### 2022-10-05 Proposal/Proposal.tex
commit #DataDescription

@@
 
+\section*{Data Description}
+I wrote SQL queries to obtain my data sets from the undisclosed finanical firm which comprise of the call center agents performance and the interactions between members. 
+The data goes back Feburary 3, 2020 to October 3, 2022. There is 466,566 observations with their respective Call Date, Caller ID, Interaction Outcome,
+Reason for calling, Wait Time, Hold Time, Talk Duration, Result of Call, and Agent ID among other things. To protect privacy, each Caller ID
+and Agent ID has been encrypted. There is a select code of symbols for Caller ID and Agent ID has been reduced to Agent 1,2,3 ... instead of 
+their names.
+
 \bibliographystyle{chicago}

### 2022-10-05 Proposal/Proposal.tex
commit #ResearchDesign

@@
 
+\section*{Research Design}
+I will be using Rstudio to create a model to forecast the call center data. I plan on doing research on previous ways call center data
+has been forecast before. I am planning on creating multiple models based on a 15 minute interval using liner regression, poisson distribution,
+and autoregressive integrated moving average (ARIMA) models \citep*{ibrahim2016modeling}. By creating figures I can
+easily describe the patterns to my audience. These methods can clearly show a pattern which I can use to back up my claims on how many 
+employees should be present at certain times. Once I can find a clear distribution to describe the call center patterns, I will be
+able to possibly going into further detail describing if there is a relationship between call length and call reason, and if all agents are
+performing at the same level. With these methods, I believe I can investigate and answer the research question.
+
 \bibliographystyle{chicago}

### 2022-10-05 Proposal/Proposal.tex
commit #Discussion

@@
 
+\section*{Discussion}
+I expect to see in an increase in calls during the early afternoon. This is typically when people have a lunch break and would have 
+easy access to call the call center. There may be in increase in the early evening after people get out of work. In regards to agent
+performance, I feel that most agents will be relatively consistent in regards to number of calls, wait time, and other factors. I believe 
+this finanical firm would have the best of the best working for them. Because I have data from 2020, that may skew the data due to the impacts
+of COVID-19. My impacts will allow this finanical firm to optimize their call center and have a more efficient and effective process. They will
+also have a better expectation of what will happen after something unexpected occurs, like a website outage. If my investigation is not what I 
+expect, I believe that would be okay because this would give a different prospectives of when and why people call. I believe the more prospective
+the more efficient the call center can be. My findings have the ability to both challenge and corroborate assumptions when it comes to the best way to 
+forecast call center data depending on my conclusions.
+
 \bibliographystyle{chicago}

### 2022-10-05 Proposal/Proposal.tex
commit #conclusion

@@
 
+\section*{Conclusion}
+Overall, my research can provide excellent insight into forecasting call center data. I can help finanical firms with ways to deal with spikes in 
+calls and how to be efficient during the least amount of activity throughout the day. I will set a new standard on how agents should be operating to set
+a baseline on performance. With the amount of data at my hands, there is also an opportunity for others to collaborate and extend this analysis after this semester.
 \bibliographystyle{chicago}

### 2022-10-05 Proposal/Proposal.tex
commit #updated

@@
 \section*{Specific Aims}
-I will be attempting to model call volume per a 15 minute interval and determining if there is any seasonality in the calls. With each interval,
+Research Question: Is there any seasonality in call center data per 15 minute intervals and what is the optimal number of employees needed per 30 minute intervals?
+I will be attempting to model call volume per a 15 minute interval and determining if there is any seasonality in the calls. With each 30 minute interval,
 I will find the optimal number of employees needed to handle the amount of incoming calls based on typical call length. This is extremely important

### 2022-10-09 Proposal/Proposal.tex
commit

@@
 \section*{Introduction}
-Call centers are a staple of the finanical industry with agents working in the United States, Europe, Asia and Africa \citep{ibrahim2016modeling}. 
+Call Centers are a staple of the finanical industry with agents working in the United States, Europe, Asia and Africa \citep{ibrahim2016modeling}. 
 Effective management is essential to running call centers and businesses are consistently trying to model and optimize when customers are calling with questions. 

### 2022-11-09 Manuscript/Manuscript.tex
commit #setup

--- 2022-10-05 Proposal/Proposal.tex
@@
 \MakeOuterQuote{"}
-\title{My Statistics 3494W Proposal}
+\title{Call Center Volume Regression Data Analysis }
 
@@
 
-\date{October 4 2022}
+\date{November 14 2022}
 
@@
 \section*{Introduction}
-Call centers are a staple of the finanical industry with agents working in the United States, Europe, Asia and Africa \citep{ibrahim2016modeling}. 
-Effective management is essential to running call centers and businesses are consistently trying to model and optimize when customers are calling with questions. 
-\citet*{evensen1999effective} describes the recent growth of call centers as being, "viewed as little more than lower cost channels for customer
-problem resolution, are quickly becoming a powerful means of service delivery with a potential for substantial revenue generation".
-I have chosen this to be my topic of study as I have a strong interest in working in the finanical industry after graduation and I have an unique opportunity to utilize real-world data from an undisclosed
-finanical firm. Due to this, My findings may provide insight that would benefit the company and its members.
 
 \section*{Specific Aims}
-I will be attempting to model call volume per a 15 minute interval and determining if there is any seasonality in the calls. With each interval,
-I will find the optimal number of employees needed to handle the amount of incoming calls based on typical call length. This is extremely important
-to be able to forecast call volume and be optimally prepared with a proper number of employees for anticipated spikes in calls. If a business is not prepared
-this will create a increase in holdtime which will result in members becoming frustrated and discouraged.
-\citet*{ibrahim2016modeling} states, "The accurate modeling and forecasting of future call arrival volumes is a
-complicated issue which is critical for making important operational decisions, such as staffing and scheduling, in the call center".
 
 \section*{Data Description}
-I wrote SQL queries to obtain my data sets from the undisclosed finanical firm which comprise of the call center agents performance and the interactions between members. 
-The data goes back Feburary 3, 2020 to October 3, 2022. There is 466,566 observations with their respective Call Date, Caller ID, Interaction Outcome,
-Reason for calling, Wait Time, Hold Time, Talk Duration, Result of Call, and Agent ID among other things. To protect privacy, each Caller ID
-and Agent ID has been encrypted. There is a select code of symbols for Caller ID and Agent ID has been reduced to Agent 1,2,3 ... instead of 
-their names.
 
 \section*{Research Design}
-I will be using Rstudio to create a model to forecast the call center data. I plan on doing research on previous ways call center data
-has been forecast before. I am planning on creating multiple models based on a 15 minute interval using liner regression, poisson distribution,
-and autoregressive integrated moving average (ARIMA) models \citep*{ibrahim2016modeling}. By creating figures I can
-easily describe the patterns to my audience. These methods can clearly show a pattern which I can use to back up my claims on how many 
-employees should be present at certain times. Once I can find a clear distribution to describe the call center patterns, I will be
-able to possibly going into further detail describing if there is a relationship between call length and call reason, and if all agents are
-performing at the same level. With these methods, I believe I can investigate and answer the research question.
 
 \section*{Discussion}
-I expect to see in an increase in calls during the early afternoon. This is typically when people have a lunch break and would have 
-easy access to call the call center. There may be in increase in the early evening after people get out of work. In regards to agent
-performance, I feel that most agents will be relatively consistent in regards to number of calls, wait time, and other factors. I believe 
-this finanical firm would have the best of the best working for them. Because I have data from 2020, that may skew the data due to the impacts
-of COVID-19. My impacts will allow this finanical firm to optimize their call center and have a more efficient and effective process. They will
-also have a better expectation of what will happen after something unexpected occurs, like a website outage. If my investigation is not what I 
-expect, I believe that would be okay because this would give a different prospectives of when and why people call. I believe the more prospective
-the more efficient the call center can be. My findings have the ability to both challenge and corroborate assumptions when it comes to the best way to 
-forecast call center data depending on my conclusions.
 
 \section*{Conclusion}
-Overall, my research can provide excellent insight into forecasting call center data. I can help finanical firms with ways to deal with spikes in 
-calls and how to be efficient during the least amount of activity throughout the day. I will set a new standard on how agents should be operating to set
-a baseline on performance. With the amount of data at my hands, there is also an opportunity for others to collaborate and extend this analysis after this semester.
 \bibliographystyle{chicago}
-\bibliography{citations.bib}
+\bibliography{Citations.bib}
 \end{document}

### 2022-11-09 Code/R Code.R
commit #Data Analysis Complete

@@ -1,0 +1,662 @@
+library(tidyverse)
+library(lubridate)
+library(ggpubr)
+library(qqplotr)
+library(hms)
+library(Hmisc)
+library(PerformanceAnalytics)
+library(dplyr)
+
+setwd("~/GitHub/Project/course-paper-or-presentation-MichaelMarcaccio/Data")
+
+orig_callData <- read.csv("CSV Interaction Call Center.csv")
+orig_agentData <- read.csv("CSV Agent Table.csv")
+
+
+callData_withTimes <- orig_callData
+
+# Use lubridate
+callData_withTimes$START15 <- mdy_hm(orig_callData$START15)
+callData_withTimes$STARTTIME <- mdy_hm(orig_callData$STARTTIME)
+callData_withTimes$ENDTIME <- mdy_hm(orig_callData$ENDTIME)
+
+range(callData_withTimes$STARTTIME) #Remove the 3rd, so ends at a full week (Saturday, November 1st, 2022)
+
+
+
+callData_withTimes <- callData_withTimes %>% mutate(StartTIME_DATEONLY = floor_date(callData_withTimes$STARTTIME, "day"))
+callData_withTimes <- callData_withTimes %>% mutate(StartTIME_DATEONLY = ymd(callData_withTimes$StartTIME_DATEONLY))
+
+str(callData_withTimes$StartTIME_DATEONLY)
+callData_withOut_10_3_22 <- callData_withTimes %>% filter(StartTIME_DATEONLY != "2022-10-03") 
+
+str(callData_withOut_10_3_22)
+
+
+
+callData_withOut_10_3_22_nChat <- callData_withOut_10_3_22 %>% filter(ï..INTERACTIONTYPE!= "Chat") 
+
+## REMOVING VARIABLES:
+removeVarList1 <- c("INTERACTIONTYPE", "CALLDATE", "INTRCREATETYPNAME", "INTR_ID", "QUEUEDYN", "INTERACTIONID", "EVOLVEID", "QUEUED", "ANSWEREDYN", 
+                    "ABANDONED", "ABANDONEDYN", "EXCLUDESERVICELEVELYN", "INTERACTIONOUTCOME...14", "LASTINTERACTIONSTATE")
+
+
[…]

### 2022-11-09 Data/Forecasting Call Volume Time Series.R

@@ -1,51 +1,0 @@
-library(readxl)
-library(dplyr)
-library(writexl)
-library(miscTools)
-library(tseries)
-library(forecast)
-library(pls)
-library(caret)
-library(expsmooth)
-
-
-setwd("~/GitHub/Project/course-paper-or-presentation-MichaelMarcaccio/Data")
-Interaction_Results<- read_excel("Excel Interaction Call Center.xlsx")
-Interation_Results<- data.frame(Interaction_Results)
-times <- read.csv("Time_Template.csv")
-times$date_time<- as.POSIXct(times$date_time,format = "%m/%d/%Y %H:%M")
-freq<-data.frame(table(Interaction_Results$START15))
-freq$Var1<- as.POSIXct(freq$Var1,tz = "EST",format = "%Y-%m-%d %H:%M")
-names(freq) <- c("date_time","Volume")
-df <-merge(times,freq,by = "date_time", all.x = TRUE)
-df[1:50970,]
-df$Volume = coalesce(df$Volume,0)
-df$value <- coalesce(df$value,0)
-df$new<-pmax(df$value,df$Volume)
-ts_freq <- ts(df$new, frequency = 365*24*2, start = c(2020,1585))
-ts_freq_train <- ts(ts_freq[1:floor(length(ts_freq)*.7)],  frequency = 365*24*2, start = c(2020,1585))
-ts_freq_test <- ts(ts_freq[ceiling(length(ts_freq)*.7):length(ts_freq)],frequency = 365*24*2, end = c(2022,17520))
-
-for (i in 0:5){
-  
-  for (d in 0:2){
-    
-    for (m in 0:5){
-      
-      fit <- arima(ts_freq_train, c(i, d, m),seasonal = list(order = c(1,0,1), period = 7*24*2), method = c('CSS'))
-      
-      pred <- predict(fit, n.ahead = (length(ts_freq)-ceiling(length(ts_freq)*.7)))
-      
-      ts_pred = ts(data = pred$pred, frequency = 365*24*2, end = c(2022,17520) )
-      
-      if(rSquared(ts_freq_test, resid = c(ts_freq_test - pred$pred)) > 0) {
-        
-        print(i)
-        
-        print(d)
-        
-        print(m)
-        
-        print(rSquared(ts_freq_test, resid = c(ts_freq_test - pred$pred)))}
-      
-    }}}

### 2022-11-11 Code/R Code.R
commit #setup

@@ -519,21 +519,28 @@ timePeriods_n213 <- forEach15MinutePeriodAllWeek2[,]
 
 weekDayPeriods_n6 <- forEachDayOfWeekTheAvgEach15MinPeriod_final
 
-#Ccorrelations
+#Correlations
 cor.test(timePeriods_n213$avgWaitTime, timePeriods_n213$avgCallTime) # good
-cor.test(weekDayPeriods_n6$avgWaitTime, weekDayPeriods_n6$avgCallTime) # not good
+cor.test(weekDayPeriods_n6$avgWaitTime, weekDayPeriods_n6$avgCallTime) # good
 
+#Add Agents to Reduce Wait Time
 cor.test(timePeriods_n213$callsPerAgent, timePeriods_n213$avgWaitTime) # good
 cor.test(weekDayPeriods_n6$callsPerAgent, weekDayPeriods_n6$avgWaitTime) # not good
 
+#Add Agents to Reduce Call Time
 cor.test(timePeriods_n213$callsPerAgent, timePeriods_n213$avgCallTime) # good
 cor.test(weekDayPeriods_n6$callsPerAgent, weekDayPeriods_n6$avgCallTime) # not good
 
+
+#Add Agents to Reduce Wait Goal Not Being Met
 cor.test(timePeriods_n213$callsPerAgent, timePeriods_n213$avgGoalMet) # good
 cor.test(weekDayPeriods_n6$callsPerAgent, weekDayPeriods_n6$avgGoalMet) # not good
 
-cor.test(timePeriods_n213$callsPerAgent, timePeriods_n213$avgInteractValue) # not good
-cor.test(weekDayPeriods_n6$callsPerAgent, weekDayPeriods_n6$avgInteractValue) # not good
+
+#Add Agents to Reduce Calls not being "Handled"
+cor.test(timePeriods_n213$callsPerAgent, timePeriods_n213$avgInteractValue) # not Good-Correlation doesnt make sense
+cor.test(weekDayPeriods_n6$callsPerAgent, weekDayPeriods_n6$avgInteractValue) # not Good
+
 
 
 # square values for polynomial relationships
@@ -560,33 +567,6 @@ summary(lm(avgGoalMet ~ callsPerAgent + callsPerAgent_sq, data = timePeriods_n21
 
 summary(lm(avgInteractValue ~ callsPerAgent, data = timePeriods_n213))
[…]

### 2022-11-11 Manuscript/Manuscript.tex
commit #Data Analysis Complete
commit #setup
commit #first paragraph of intro

@@
 \MakeOuterQuote{"}
-\title{Call Center Volume Regression Data Analysis }
+\title{Call Center Regression Data Analysis}
 
@@
 
+\begin{abstract}
+ With over 15 million people employed, a compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and 28,000
+ in the United States alone, call centers play a pivotal role in a businesses success.In this paper, call center volume was forecasted and
+ models were created to predict the number of agents needed to meet critical attributes such as waittime, calltime, and holdtime. 
+ Forecasting gives businesses the ability to make informed business decision and develop data-driven strategies. In the literature it is very
+ common to see call center volume being predicted using different techniques, but there is very limited studies on attempting to correlate
+ the number of agents needed. Through Regression techniques, there are 8 models proposed to model the number of agents needed based on waittime,
+ calltime, goaltime, and the amount of calls handled.
+\end{abstract}
+
 \section*{Introduction}
-
-\section*{Specific Aims}
+With over 15 million people employed, a compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and 28,000
+in the United States alone, call centers play a pivotal role in a businesses success. Call Centers are a key part of customer service,
+that will save a company time, money, and unneccessary stress. In the banking industry, calls can range from inquires, transfers, 
+payments, reporting, to processing. This means members can be calling about their account balance, credit card bills, loan applications, 
+or unauthorized transactions. It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of the bank.
 
@@
 
-\section*{Research Design}
+\section*{Methods}
+Test stuffg
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=200pt,height=200pt]{By Year.png}
+    \caption{This is my first figure.}
+    \label{fig:Year}
+  \end{figure}
+
+\section*{Results}
+\citep{avramidis2005modeling}
+\citep{evensen1999effective}
+\citep{ibrahim2016modeling}
 
@@
 
-\section*{Conclusion}
 \bibliographystyle{chicago}

### 2022-11-11 Manuscript/Manuscript.tex
commit #second and three paragraph

@@
 \usepackage[autostyle, english = american]{csquotes}
+\usepackage{underscore}
 \MakeOuterQuote{"}
@@
 
+  Many studies have been done working with call centers such as Modeling and Forecasting Call Center Arrivals \citep{ibrahim2016modeling}.
+Here an Autoregressive moving average (ARIMA) model is used, which is depicted in the paper as:
+\begin{equation}
+  \label{eq:ARIMA Standard}
+  \Phi(B)(x_i -\mu)=\theta_q(B)\varepsilon_t
+\end{equation}
+Ibrahim uses multiple ARIMA models to depict seasonality with a combonination of exponential smoothing. Holt-Winters smoothing is also used,
+with three equations of:
+\begin{equation}
+  \label{eq:Holt-Winters}
+  M_t=\alpha_0(X_t-S_{t-s}) + (1-\alpha_0)(M_{t-1}+B_{t-1}),
+\end{equation}
+\begin{equation}
+  \label{eq:Holt-Winters2}
+  B_t=\alpha_1(M_t-M_{t-1}) +(1-\alpha_1)B_{t-1},
+\end{equation}
+\begin{equation}
+  \label{eq:Holt-Winters3}
+  S_t=\alpha_2(X_t-M_t) +(1-\alpha_2)S_{t-s},
+\end{equation}
+where $B_{t}$ is the slope component, $M_{t}$ is the level component, and $S_{t}$ is the seasonal component, and s is the period of seasonality.
+Arima models are a great model to create as "they allow the  representation of a  wide array of potentially useful predictor functions in  models  which contain relatively few parameters" \citep{newbold1983arima}.
+With the combination of Holt-Winters smoothing, Ibrahim creates a great model for forecasting call volume, however he never goes into detail about
+how many agents there should be.
+
+  \citep{evensen1999effective} goes into detail about effectve service delivery stating the expecations of customers are of "function of
+the customer's own experiences...and when judging their own service quality, financial instiutions need to evalute themselves on 
+objective measures which span across industries". When taking this into consideration, I focused my models on using calls per agent approach,
+so agents are not overworked and can treat each member with respect and honor to represent the business in good light. \citep{avramidis2005modeling} confirms
+this as it is described as the "call-to-agent" problem, and that an efficiency-driven call center is important.
+
+  The contributions of the paper
+
 \section*{Data Description}
@@
 
+\section*{Results}
+
 \section*{Discussion}

### 2022-11-11 Manuscript/Manuscript.tex
commit #Introduction

@@
 the customer's own experiences...and when judging their own service quality, financial instiutions need to evalute themselves on 
-objective measures which span across industries". When taking this into consideration, I focused my models on using calls per agent approach,
+objective measures which span across industries".When taking this into consideration, I focused my models on using a calls per agent approach,
 so agents are not overworked and can treat each member with respect and honor to represent the business in good light. \citep{avramidis2005modeling} confirms
@@
 
-  The contributions of the paper
+  The contributions of the paper creates models on the basis to maximize quality of the service in relation to the number of agents. 
+Based on this, models were created to minimize:
+1)WaitTime
+2)CallTime
+3)Reduce GoalTime not being Met
+4)Reduce Calls not being Handled
+The rest of the paper will go through the dataset and breaking it up to present a clear view on the historical data. I have also created a 
+forecast on the projected call volume throughout a week through a 15 minute interval.
 
@@
 \section*{Results}
-\citep{avramidis2005modeling}
-\citep{evensen1999effective}
-\citep{ibrahim2016modeling}
 

### 2022-11-11 Manuscript/Manuscript.tex
commit #Middle of Data

@@
 
-  Many studies have been done working with call centers such as Modeling and Forecasting Call Center Arrivals \citep{ibrahim2016modeling}.
+  Many studies have been done working with call center volumes such as Modeling and Forecasting Call Center Arrivals \citep{ibrahim2016modeling}.
 Here an Autoregressive moving average (ARIMA) model is used, which is depicted in the paper as:
@@
 Arima models are a great model to create as "they allow the  representation of a  wide array of potentially useful predictor functions in  models  which contain relatively few parameters" \citep{newbold1983arima}.
-With the combination of Holt-Winters smoothing, Ibrahim creates a great model for forecasting call volume, however he never goes into detail about
+With the combination of Holt-Winters smoothing, Ibrahim creates a great model for forecasting call volume, however the paper never goes into detail about
 how many agents there should be.
@@
 Based on this, models were created to minimize:
-1)WaitTime
-2)CallTime
-3)Reduce GoalTime not being Met
-4)Reduce Calls not being Handled
+\begin{enumerate}
+  \item WaitTime
+  \item CallTime
+  \item Reduce GoalTime not being Met
+  \item Reduce Calls not being Handled
+\end{enumerate}
 The rest of the paper will go through the dataset and breaking it up to present a clear view on the historical data. I have also created a 
@@
 
-\section*{Data Description}
+\section*{Data}
+\begin{sloppypar}
+  The data comes from an undisclosed bank where I wrote two SQL queries to obtain. This comes directly from the banks records dating back from Febuary 2020
+  to Septemeber 2022, and I was lucky enough to do a data analysis on real-life data. This dataset consists of 466,565 observations of 31 variables. 
+  Some significant variables consist of Calldate, Caller_ID, Caller_ID, QueuedYN, AnsweredYN, AbandonedYN, QueuedName, InteractionOutcome, 
+  AnsweredGoalMet, StartTime, EndTime, WaitTime, Holdtime, AgentTalkDuration, AgentHandleTime, WrapUpTime, DayoftheYear,
+  WeekoftheYear, and NbrofAgents.
+\end{sloppypar}
+  It is important to note that AgentTalkDuration refers to the actual amount of time the agent the agent was talking while
+AbandonedYN refers to if the caller ended the call before speaking to a representative. The QueuedYN is if the member was put in a queue and had to wait to speak to an agent.
+The queue is an automated service or an IVR (Interactive Voice Response). The latest generation of speech-recognition technology allows
+IVRs to interpret complex user commands, so customers may be able to “self-serve”, i.e., complete the service interaction at the IVR. \citep{avramidis2005modeling}.
+Holdtime is how long the member waits when an agent places on them hold, while waittime is how long they have to wait before someone answers there call.
+WrapUpTime refers to how long the member takes to hang up the phone after the agent stops talk. AgentHandleTime is the total of Holdtime, WrapUpTime, and AgentHandleTime.
 
 \section*{Methods}
-Test stuffg
 \begin{figure}[H]
@@
 
-\section*{Results}
-
-\section*{Results}
+\section*{Simulation}
 

### 2022-11-11 Manuscript/Manuscript.tex
commit #cleanup -midway through data

@@
 \begin{abstract}
- With over 15 million people employed, a compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and 28,000
- in the United States alone, call centers play a pivotal role in a businesses success.In this paper, call center volume was forecasted and
+ With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
+ in the United States alone, call centers play a pivotal role in a business' success.In this paper, call center volume was forecasted and
  models were created to predict the number of agents needed to meet critical attributes such as waittime, calltime, and holdtime. 
@@
 \section*{Introduction}
-  With over 15 million people employed, a compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and 28,000
-in the United States alone, call centers play a pivotal role in a businesses success. Call Centers are a key part of customer service,
-that will save a company time, money, and unneccessary stress. In the banking industry, calls can range from inquires, transfers, 
-payments, reporting, to processing. This means members can be calling about their account balance, credit card bills, loan applications, 
-or unauthorized transactions. It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of the bank.
+  With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
+in the United States alone, call centers play a pivotal role in a business' success. Call centers are a key part of customer service
+that will save a company time, money, and unneccessary obstacles. In the banking industry, calls can range from inquires, transfers, 
+payments, reporting, to processing. This means members could call about their account balance, credit card bills, loan applications, 
+or unauthorized transactions. It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of banking.
 
-  Many studies have been done working with call center volumes such as Modeling and Forecasting Call Center Arrivals \citep{ibrahim2016modeling}.
+  Many studies have been done working with call center volumes as presented in Modeling and Forecasting Call Center Arrivals \citep{ibrahim2016modeling}.
 Here an Autoregressive moving average (ARIMA) model is used, which is depicted in the paper as:
@@
 \end{equation}
-Ibrahim uses multiple ARIMA models to depict seasonality with a combonination of exponential smoothing. Holt-Winters smoothing is also used,
+Ibrahim uses multiple ARIMA models to depict seasonality with a combination of exponential smoothing. Holt-Winters smoothing is also used,
 with three equations of:
@@
 \end{equation}
-where $B_{t}$ is the slope component, $M_{t}$ is the level component, and $S_{t}$ is the seasonal component, and s is the period of seasonality.
-Arima models are a great model to create as "they allow the  representation of a  wide array of potentially useful predictor functions in  models  which contain relatively few parameters" \citep{newbold1983arima}.
+where $B_{t}$ is the slope component, $M_{t}$ is the level component, $S_{t}$ is the seasonal component, and s is the period of seasonality.
+ARIMA models are a great model to create as "they allow the  representation of a  wide array of potentially useful predictor functions in  models  which contain relatively few parameters" \citep{newbold1983arima}.
 With the combination of Holt-Winters smoothing, Ibrahim creates a great model for forecasting call volume, however the paper never goes into detail about
-how many agents there should be.
+how many agents there should be working at a set time.
 
-  \citep{evensen1999effective} goes into detail about effectve service delivery stating the expecations of customers are of "function of
+  \citep{evensen1999effective} goes into detail about effective service delivery stating the expectations of customers are a "function of
 the customer's own experiences...and when judging their own service quality, financial instiutions need to evalute themselves on 
 objective measures which span across industries".When taking this into consideration, I focused my models on using a calls per agent approach,
-so agents are not overworked and can treat each member with respect and honor to represent the business in good light. \citep{avramidis2005modeling} confirms
-this as it is described as the "call-to-agent" problem, and that an efficiency-driven call center is important.
+so agents are not overworked and can treat each caller with respect while answering their concerns in a timely manner to represent the business in a good light. \citep{avramidis2005modeling} confirms
+this as it is described as the "call-to-agent assignment problem", and that an efficiency-driven call center is important.
 
-  The contributions of the paper creates models on the basis to maximize quality of the service in relation to the number of agents. 
+  The contributions of the paper creates models on the basis to maximize quality of service in relation to the number of agents. 
 Based on this, models were created to minimize:
 \begin{enumerate}
-  \item WaitTime
-  \item CallTime
-  \item Reduce GoalTime not being Met
-  \item Reduce Calls not being Handled
+  \item Wait Time
+  \item Call Time
+  \item Reduce the Amount of Agent Handle Time
+  \item Reduce the Amount of Calls not being handled
 \end{enumerate}
-The rest of the paper will go through the dataset and breaking it up to present a clear view on the historical data. I have also created a 
-forecast on the projected call volume throughout a week through a 15 minute interval.
+The remainder of the paper will present the dataset and break it into a clear view on the historical data. I have also created a 
+forecast on the projected call volume throughout a week on 15 minute intervals.
 
@@
 \end{sloppypar}
-  It is important to note that AgentTalkDuration refers to the actual amount of time the agent the agent was talking while
+  It is important to acknowledge that AgentTalkDuration refers to the actual amount of time the agent the agent was talking while
 AbandonedYN refers to if the caller ended the call before speaking to a representative. The QueuedYN is if the member was put in a queue and had to wait to speak to an agent.
@@
 Holdtime is how long the member waits when an agent places on them hold, while waittime is how long they have to wait before someone answers there call.
-WrapUpTime refers to how long the member takes to hang up the phone after the agent stops talk. AgentHandleTime is the total of Holdtime, WrapUpTime, and AgentHandleTime.
+WrapUpTime refers to how long the member takes to hang up the phone after the agent stops talk. AgentHandleTime is the total of Holdtime, WrapUpTime, and AgentTalkDuration combined.
 

### 2022-11-11 Code/R Code.R
commit #update

@@ -74,7 +74,7 @@ INTERACTIONOUTCOME_times <- callData_rduce2 %>%
                    wrap_avg = mean(WRAPUPTIME), 
                    totalTalk_avg = mean(AGENTHANDLETIME))
 
-
+INTERACTIONOUTCOME_times
 
 
 

### 2022-11-12 Manuscript/Manuscript.tex
commit #starting methods

@@
 \usepackage{graphicx}
+\usepackage{multirow}
 \usepackage{natbib}
+\usepackage{tabularx} 
 \usepackage{enumitem}
+\usepackage{array}
 \usepackage{booktabs}
@@
 
-\section*{Methods}
+  This data is allows me to easily answer the research question as I am using real-life data. With a huge sample size and many variables,
+there is a great opportunity for data analysis and modeling. With this dataset, I know when doing calculations such as finding means and creating plots, 
+they will able to accurately give a truly image of call center volume and agent information to a small period of time such as 15 minutes.
+  I did do some exploratory data analysis by creating figures that represent call center volume by the year, month, day of week, and time. 
+I also created a tabled that shows the average wait time, talk time, hold time, wrap up time, and count of every interaction Outcome.
 \begin{figure}[H]
   \centering
-    \includegraphics[width=200pt,height=200pt]{By Year.png}
-    \caption{This is my first figure.}
+  \includegraphics[width=\textwidth]{By Year.png}
+  \caption{Call Volume Grouped by Year.}
   \label{fig:Year}
 \end{figure}
+Here we can see that 2021 has the highest call volume. Please Note that 2020 only has 11 months, while 2020 only has 10. This may be why the data appears skewed.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{ByMonthVolume.png}
+  \caption{Call Volume Grouped by Month.}
+  \label{fig:Month}
+\end{figure}
+When grouped by month, we can see an interesting peak around April. This may be because that is tax season and members are calling for tax information.
+Also April 2020 may have a higher peak than April 2021, due to COVID-19. During that time, many individuals were eligble for a 1,200 dollar stimulus check.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{CallVolumeByDayOfWeek.png}
+  \caption{Call Volume Grouped by Day.}
+  \label{fig:Day}
+\end{figure}
+With Sunday representing 1, we can see that most calls happen on a Friday. Saturday has an extremely low count. This can be explained due to the
+varying hours of the call center. Monday through Thursday, the call center is open 8am to 5pm, a total of 9 hours. Friday the call center is open
+8am-7pm, a total of 11 hours. Saturday the call center is only open 8:30 am to 12pm, a total of 3 and a half hours.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{CallVolumeByTimeOfDayGROUPEDbyYear.png}
+  \caption{Call Volume Grouped by Time.}
+  \label{fig:Timeoneday}
+\end{figure}
+The call center consistently has a spike around 9am throughout the 3 years. This is suprising as the call center opens at 8am. This is important to be aware of when
+creating a forecasting model and having the banks employees be at their station at 9am. The decreasing trend throughout the day is not suprising
+as most people are working throughout the day.
+\begin{table}[H]
+  \resizebox{\textwidth}{!} {
+  \begin{tabular}{ l | l | l | l | l | l | l}
+    {\bf Outcome} & {\bf Count} & {\bf Wait Avg} & {\bf Talk Avg} & {\bf Hold Avg} & {\bf Wrap Avg} & {\bf Total Talk Avg} \\
+  \hline
+  Abandoned & 2364 & 100 & 11.3 & 0.06 & 2.40 & 13.8 \\
+  \hline
+  Handled & 460047 & 107 & 253 & 26.2 & 16.3 & 295\\
+  \hline
+  Leave Number & 411 & 214 & 66 & 6.18 & 7.80 & 80\\
+  \hline
+  Not Specified & 299 & 1.21 & 120 & 0.278 & 3.24 & 123\\
+  \hline
+  Service Unavailable & 1 & 0 & 0 & 0 & 0 & 0\\
+  \hline
+  Wrong Number & 3 & 357 & 0 & 0 & 12 & 12\\
+  \end{tabular}
+  }
+  \end{table}
+Here it is prevalent that a majority of calls are handled. These variables played a key part in my models for the agents.
+\section*{Methods}
+I created linear models to show the relationship between calls per agent and average waitime, holdtime, average goal met, and average 
+interaction value. Average goal met was a variable created in relationship to the AnsweredGoalMet. AnsweredGoalMet was given in 1 and 0s, 
+1 if the goal was hit and 0 if it was not hit. This variable is very fluid, as each company has its own reasoning for what they want their
+goal time to be. Average Interaction Value was based off a variable that was created based on the InteractionOutcome. "Handled "got assigned 
+1 as it was a positive outcome and -1 for "Abandoned" and "Leave Number" as they were deemed negative. The others were considered neutral, for example
+"Not Specified", was given a 0. 
+Linear Regression is based off five key assumptions, there is a linear relationship, multivariate normality, No or little multicollinearity, No auto-correlation, 
+and Homoscedasticity. multicollinearity refers to
 

### 2022-11-12 Manuscript/Manuscript.tex
commit #begining simulation

--- 2022-11-11 Manuscript/Manuscript.tex
@@
 
-\section*{Methods}
+  This data is allows me to easily answer the research question as I am using real-life data. With a huge sample size and many variables,
+this is a great opportunity for data analysis and modeling. With this dataset, I know when doing calculations such as finding means and creating plots, 
+I will able to accurately give a truly image of call center volume and agent information to a small period of time such as 15 minutes.
+  I did do some exploratory data analysis by creating figures that represent call center volume by the year, month, day of week, and time. 
+I also created a tabled that shows the average wait time, talk time, hold time, wrap up time, and count of every Interaction Outcome.
 \begin{figure}[H]
   \centering
-    \includegraphics[width=200pt,height=200pt]{By Year.png}
-    \caption{This is my first figure.}
+  \includegraphics[width=\textwidth]{By Year.png}
+  \caption{Call Volume Grouped by Year.}
   \label{fig:Year}
 \end{figure}
+Here we can see that 2021 has the highest call volume. Please Note that 2020 only has 11 months, while 2020 only has 10. This may be why the data appears skewed.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{ByMonthVolume.png}
+  \caption{Call Volume Grouped by Month.}
+  \label{fig:Month}
+\end{figure}
+When grouped by month, we can see an interesting peak around April. This may be because that is tax season and members are calling for tax information.
+Also April 2020 may have a higher peak than April 2021, due to COVID-19. During that time, many individuals were eligble for a 1,200 dollar stimulus check.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{CallVolumeByDayOfWeek.png}
+  \caption{Call Volume Grouped by Day.}
+  \label{fig:Day}
+\end{figure}
+With Sunday representing 1, we can see that most calls happen on a Friday. Saturday has an extremely low count. This can be explained due to the
+varying hours of the call center. Monday through Thursday, the call center is open 8am to 5pm, a total of 9 hours. Friday the call center is open
+8am-7pm, a total of 11 hours. Saturday the call center is only open 8:30 am to 12pm, a total of 3 and a half hours.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{CallVolumeByTimeOfDayGROUPEDbyYear.png}
+  \caption{Call Volume Grouped by Time.}
+  \label{fig:Timeoneday}
+\end{figure}
+The call center consistently has a spike around 9am throughout the 3 years. This is suprising as the call center opens at 8am. This is important to be aware of when
+creating a forecasting model and having the banks employees be at their station at 9am. The decreasing trend throughout the day is not suprising
+as most people are working throughout the day.
+\begin{table}[H]
+  \resizebox{\textwidth}{!} {
+  \begin{tabular}{ l | l | l | l | l | l | l}
+    {\bf Outcome} & {\bf Count} & {\bf Wait Avg} & {\bf Talk Avg} & {\bf Hold Avg} & {\bf Wrap Avg} & {\bf Total Talk Avg} \\
+  \hline
+  Abandoned & 2364 & 100 & 11.3 & 0.06 & 2.40 & 13.8 \\
+  \hline
+  Handled & 460047 & 107 & 253 & 26.2 & 16.3 & 295\\
+  \hline
+  Leave Number & 411 & 214 & 66 & 6.18 & 7.80 & 80\\
+  \hline
+  Not Specified & 299 & 1.21 & 120 & 0.278 & 3.24 & 123\\
+  \hline
+  Service Unavailable & 1 & 0 & 0 & 0 & 0 & 0\\
+  \hline
+  Wrong Number & 3 & 357 & 0 & 0 & 12 & 12\\
+  \end{tabular}
+  }
+  \end{table}
+Here it is prevalent that a majority of calls are handled. These variables played a key part in my models for the agents.
+\section*{Methods}
+When seeing these patterns, I did not see much seasonality in the data. While there was a clear jump in volume based on time, I did not see much in regards
+to year, month, or day. I then confirmed this by making one last histogram.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{SeasonalityOfCallVolume.png}
+  \caption{Seasonality Of Call Volume .}
+  \label{fig:Seasonality}
+\end{figure}
+Here we do not see any clear pattern based on whether its winter, spring, summer, or fall. Overall, this was not too surpising.
 
+I also created linear models to show the relationship between calls per agent and average waitime, holdtime, average goal met, and average 
+interaction value. Average goal met was a variable created in relationship to the AnsweredGoalMet. AnsweredGoalMet was given in 1 and 0s, 
+1 if the goal was hit and 0 if it was not hit. This variable is very fluid, as each company has its own reasoning for what they want their
+goal time to be. Average Interaction Value was based off a variable that was created based on the InteractionOutcome. "Handled "got assigned 
+1 as it was a positive outcome and -1 for "Abandoned" and "Leave Number" as they were deemed negative. The others were considered neutral, for example
+"Not Specified", was given a 0.
+
+  Linear Regression is based off five key assumptions,
+  \begin{enumerate}
+  \item There is a Linear relationship,
+  \item Multivariate normality,
+  \item No or Little multicollinearity,
+  \item No auto-correlation,
+\end{enumerate} Multicollinearity refers to the occurrence of high intercorrelations among two or more independent variables in a multiple regression model.
+To prevent this, I soley focus on one variable at a time when making my models on agents. Homoscedasticity is an assumption there is equal or similar variances in different groups being compared.
+From here I then did a Correlation Plot:
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{Correlation.png}
+  \caption{Correlation Between Variables.}
+  \label{fig:Correlation}
+
+Here we see that correlations between Average Wait Time, Average Handle Time, Average Answer Goal Time, Average Score Answer Goal Time Met, and Ratio Calls Per Agent.
+We see that Calls Per Agent is correlated with all 4 variables in our models which was a great step to acheive.
+I then checked to see what the distribution was between calls per agent was throughout each day.
+  \begin{table}[H]
+    \resizebox{\textwidth}{!} {
+    \begin{tabular}{ l | l | l | l | l |}
+      {\bf DayofWeek} & {\bf AvgNumCalls} & {\bf AvgNumAgents} & {\bf CallsPerAgent} & {\bf Num15Periods} \\
+    \hline
+    2 & 3.17 & 10.3 & 0.308 & 38 \\
+    \hline
+    3 & 3.25 & 9.81 & 0.331 & 39 \\
+    \hline
+    4 & 3.17 & 10.4 & 0.305 & 38 \\
+    \hline
+    5 & 3.08 & 10.1 & 0.306 & 37 \\
+    \hline
+    6 & 3.83 & 8.82 & 0.435 & 46 \\
+    \hline
+    7 & 1.25 & 6.33  & 0.197 & 15 \\
+    \end{tabular}
+    }
+    \end{table}
+\end{figure}
+Here we see that the Calls Per Agent is highest on Friday. This further proves that Friday is the busiest. Note that these are on 15 minute intervals,
+so for example, the call center gets 3.17 calls every 15 minutes on average on a Monday. It was surpising to see that Friday was the second
+lowest staffed day of the week. A possible suggestion to the company would be add an agent on Friday. Members may be calling about last minute
+questions on Friday to enjoy the weekend and not have to call Saturday. In regards to Saturday, it is clear that is the least busiest day of the week,
+this is not too suprising as many people like to sleep in on the weekends and not worry about financial issues. Monday through Thursday is relatively
+consistant in all aspects. Note that the reason why the "num15minPeriods" variable is not the same is due to the outliers in the dataset where individuals
+called either slightly before or after call center hours.
 \section*{Simulation}
+After seeing how consistent the call volume was, I decided to create a table and g
 

### 2022-11-12 Manuscript/Manuscript.tex
commit #finish forecast table

@@
   \item No auto-correlation,
+  \item Homoscedasticity
 \end{enumerate} Multicollinearity refers to the occurrence of high intercorrelations among two or more independent variables in a multiple regression model.
@@
   \label{fig:Correlation}
-
+\end{figure}
 Here we see that correlations between Average Wait Time, Average Handle Time, Average Answer Goal Time, Average Score Answer Goal Time Met, and Ratio Calls Per Agent.
@@
     \end{table}
-\end{figure}
 Here we see that the Calls Per Agent is highest on Friday. This further proves that Friday is the busiest. Note that these are on 15 minute intervals,
@@
 \section*{Simulation}
-After seeing how consistent the call volume was, I decided to create a table and g
+After seeing how consistent the call volume was and how big of a sample size I had, I decided to create a table and go off total calls and use averages to project call volume per weekday with the 
+created variable called RatioDayPerWeek.
+This variable is the ratio of how many hours the call center was open historically on the day(Monday,Tuesday,Wednesday...) compared to all the total hours of all days.
+I was able to produce this table:
+\begin{table}[H]
+  \resizebox{\textwidth}{!} {
+  \begin{tabular}{ l | l | l | l | l |}
+    {\bf DayofWeek} & {\bf numberofCalls} & {\bf AvgCallsPerDay} & {\bf RatioDayPerWeek} & {\bf ProjectedCallsPerDay} \\
+  \hline
+  2 & 79785 & 670 & 0.193 & 642 \\
+  \hline
+  3 & 89121 & 655 & 0.188 & 628 \\
+  \hline
+  4 & 89428 & 653 & 0.188 & 625 \\
+  \hline
+  5 & 84918 & 624 & 0.180 & 598 \\
+  \hline
+  6 & 95588 & 693 & 0.199 & 664 \\
+  \hline
+  7 & 24285 & 183 & 0.0525 & 175\\
+  \end{tabular}
+  }
+  \end{table}
+This table shows that Friday accounts for 19.9 percent of all the hours in the week the call center is open, while Saturday only accounts
+5.25 percent of the hours. The only difference there is a different in ratio for Monday thru Thursday must be holidays, e.g. Thanksgiving. 
+The Projected Calls Per Day simply came from the total calls per week * the RatioDayPerWeek. We can also see this approach worked relatively well in the forecasting model. 
+We also see that the MAPE(Mean Absolute Percent Error) is 4.21 percent. For context, a MAPE score less than 5 is very accurate.
 

### 2022-11-12 Manuscript/Manuscript.tex
commit #starting correlation

@@
   \end{table}
-Here it is prevalent that a majority of calls are handled. These variables played a key part in my models for the agents.
+Here it is prevalent that a majority of calls are handled. These variables played a key part in my models for the agents. It is also to see that 
+100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. 
 \section*{Methods}
@@
 
+  Using this information, I was able to create a figure that showed the amount of expected calls per day per 15 minute intervals. 
+  \begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{Forecast15MinPeriods.png}
+    \caption{This is the Forecast Per Day On a 15 Minute Intervals.}
+    \label{fig:Forecast}
+  \end{figure}
+Here we see that distinct pattern similar to the historical graph. The graph peaks at 9am and then slowly trails throughout the day.
+Note that the different colors represent the different days.
+
+In regards to forecasting the number of agents, I create one last table to see if there is a difference in AgentHandleTime and WaitTime
+by each 15 minute interval.
+\begin{table}[H]
+  \resizebox{\textwidth}{!} {
+  \begin{tabular}{ l | l | l | l | l | l | l |}
+    {\bf DayofWeek} & {\bf AvgNumCalls} & {\bf AvgNumAgents} & {\bf CallsPerAgent} & {\bf AvgAgentHandleTime} & {\bf AvgWaittime} & {\bf AvgInteractionValue}\\
+  \hline
+  2 & 2418 & 10.6 & 227 & 303 & 175 & 0.987 \\
+  \hline
+  3 & 2701 & 10.4 & 260 & 297 & 126 7 0.998\\
+  \hline
+  4 & 2710 & 10.7 & 254 & 297 & 80.9 & 0.987 \\
+  \hline
+  5 & 2573 & 10.2 & 253 & 289 & 87.1 & 0.988 \\
+  \hline
+  6 & 2897 & 9.93 & 292 & 293 & 88.2 & 0.987 \\
+  \hline
+  7 & 736 & 6.34 & 116 & 260 & 57.4 & 0.989\\
+  \end{tabular}
+  }
+  \end{table}
+Overall, we see that Friday continues to be the busiest days in terms of call volume but the least staffed days. However, a glaring note
+is how high the average waittime on Monday is. This may be suggesting that the subject matter of calls on Monday are more intense and urgent
+then the subject matter on a day like Saturday. With such a high wait time but not a bigger handle time, this also may be suggesting that
+employees are getting stressed out at lot more and may need more time to get themselves mentality ready to take the next call. It might be a good idea to add another employee for Mondays. 
+The other days appear to be relatively normal and Saturday is functioning very efficiently. With a waittime less than 60 seconds, there is no reason to change the staffing model for
+Saturday.
+
+Next were Correlation tests
+
 \section*{Discussion}

### 2022-11-12 Manuscript/Manuscript.tex
commit #onto models

@@
 To prevent this, I soley focus on one variable at a time when making my models on agents. Homoscedasticity is an assumption there is equal or similar variances in different groups being compared.
+I used Pearson's correlation which states the following assumptions,
+\begin{enumerate}
+  \item The Variables must be continous,
+  \item The Variables are paired,
+  \item There should be an independece of cases,
+  \item Both Variables should follow a normal distribution,
+  \item There should be a linear relationship,
+  \item Homoscedasticity,
+  \item There should be no outliers,
+\end{enumerate}
 From here I then did a Correlation Plot:
@@
   \hline
-  3 & 2701 & 10.4 & 260 & 297 & 126 7 0.998\\
+  3 & 2701 & 10.4 & 260 & 297 & 126 & 0.998\\
   \hline
@@
 
-Next were Correlation tests
-
+  From there I ran Correlation between CallsPerAgent and the dependent variables.
+The Pearson Product Moment Correlation test can take a range of values from 1 to -1.
+A value of 0 shows there is no association between two variables.
+A value greater than 0 indicates a positive association, meaning as the value of the dependent variable increases so does the independent variable.
+A value less than 0 indicates a negative association, meaning as the dependent
+variable decreases so does the independent variable.
+The stronger the correlation between the variables the higher it is to 1 or -1.
+The 4 dependent variables were Average Wait Time, Average Call Time, Average Goal Being Met, Average Interaction Value.
+The one dependent variable is CallsPerAgent. In this case, the Calltime is the same as Handletime, which is the combination of Wait time, Hold time, and Wrap Up Time. 
+The Average Goal Being Met would be whatever the business establishes in seconds of  how long they would want a call center call to last. Average Interaction Value would be at what percentage 
+they want calls being "Handled" or taken by an agent in anyway. 
+\begin{table}[H]
+  \resizebox{\textwidth}{!} {
+  \begin{tabular}{ l | l |}
+    {\bf Dependent Variable} & {\bf Correlation Coefficient}\\
+  \hline
+  Wait Time& 0.405 \\
+  \hline
+  Call Time& 0.238\\
+  \hline
+  Goal Met& -0.496  \\
+  \hline
+  Interaction Value& 0.484\\
+  \end{tabular}
+  }
+  \end{table}
+Typically, a Pearson's coefficient ranging between plus or minus .3 represents a small association, while a Pearson's coefficient
+ranging between plus or minus .3 to .5 represents a medium association, and anything over plus or minus .5 represents a large association.
+Wait Time and Calls Per Agent have a medium positive relationship which states as Calls Per Agent increases, so does the Wait Time for 
+each Caller. Call Time and Calls Per Agent have a small positive relationship which states as Calls Per Agent increases, so does the 
+Call Time. Goal Time and Calls Per Agents have the strongest relationship, in this case a negative medium relationship, which states as
+Calls Per Agents increases, the Goal Being Met decreases. This means the Average Goal Time is nothing being hit consistently when Calls 
+are increasing. Interaction Value and Calls Per Agent have a medium positive relationship. However, in theory, as calls increase there should
+be more abandoned calls, but according to Pearsons Coefficient this is not the case. So while this relationship may not be a linear one,
+I will still present a model for it.
 \section*{Discussion}

### 2022-11-12 Manuscript/Manuscript.tex
commit #discussion
commit

@@
 in the United States alone, call centers play a pivotal role in a business' success. Call centers are a key part of customer service
-that will save a company time, money, and unneccessary obstacles. In the banking industry, calls can range from inquires, transfers, 
-payments, reporting, to processing. This means members could call about their account balance, credit card bills, loan applications, 
-or unauthorized transactions. It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of banking.
+that will save a company time, money, and unneccessary obstacles.
+\citep{feinberg2002operational} claims call centers serve as a source of service recovery, added value, market intelligence, and strategic advantage
+In the banking industry, calls can range from inquires, transfers, payments, reporting, to processing. This means members could call about their account balance, credit card bills, loan applications, 
+or unauthorized transactions.
+It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of banking and are capable of handling customer impatience.
+\citep{brown2005statistical}
 
@@
   I did do some exploratory data analysis by creating figures that represent call center volume by the year, month, day of week, and time. 
-I also created a tabled that shows the average wait time, talk time, hold time, wrap up time, and count of every Interaction Outcome.
+I also created a table that shows the average wait time, talk time, hold time, wrap up time, and count of every Interaction Outcome.
 \begin{figure}[H]
@@
 creating a forecasting model and having the banks employees be at their station at 9am. The decreasing trend throughout the day is not suprising
-as most people are working throughout the day.
+as most people are working throughout the day. From a managers view, important to have your best employees not on break during that time so they are ready to solve 
+any complications that come up. \citep{rafaeli2008impact}
 \begin{table}[H]
@@
 Here it is prevalent that a majority of calls are handled. These variables played a key part in my models for the agents. It is also to see that 
-100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. 
+100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. While 
+the number itself is not significant, Avramidis explains that "The maximal time a customer is willing to wait in queue is his patience time, A, also known as time-to-abandonment. The
+time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever V > W), or beginning of service (V = W).
+In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing seconds
+in waittime could allow for a more efficient contact call system.
 \section*{Methods}
@@
 To prevent this, I soley focus on one variable at a time when making my models on agents. Homoscedasticity is an assumption there is equal or similar variances in different groups being compared.
-I used Pearson's correlation which states the following assumptions,
+Logistic and Linear Regression Assumptions: Violation Recognition and Control goes into detail about this stating, "it is necessary to make a note about sample size for this type of regression model.
+In Linear
+regression the sample size rule of thumb is that the regression analysis requires at least 20 cases per
+independent variable in the analysis"\citep{schreiber2018logistic} 
+I also used Pearson's correlation which states the following assumptions,
 \begin{enumerate}
@@
 \end{enumerate}
+The Pearsons coefficient is given below:
+\begin{equation}
+  \label{eq:Pearson}
+r= \Sigma((x_i - \bar{x})(y_i-\bar{y}))/(\sqrt{\Sigma{(x_i-\bar{x})^2}\Sigma{(y_i-\bar{y})^2}}),
+\end{equation}
 From here I then did a Correlation Plot:
@@
 
-In regards to forecasting the number of agents, I create one last table to see if there is a difference in AgentHandleTime and WaitTime
+In regards to forecasting the number of agents, I created one last table to see if there is a difference in AgentHandleTime and WaitTime
 by each 15 minute interval.
@@
 I will still present a model for it.
+
+  Here are the linear models:
+  \begin{equation}
+    \label{eq:Wait Time}
+  AvgWaittime= -5.292 + 61.148*CallsPerAgent,
+  \end{equation}
+  \begin{equation}
+    \label{eq:Call Time}
+  AvgCallTime = -256.252 + 20.115*CallsPerAgent,
+  \end{equation}
+  \begin{equation}
+    \label{eq:Goal Met}
+  AvgGoalMet= 0.986 - 0.216*CallsPerAgent,
+  \end{equation}
+  \begin{equation}
+    \label{eq:InteractionValue}
+  AvgInteractionValue= 0.97 + 0.00989*CallsPerAgent,
+  \end{equation}
+
+  \begin{table}[H]
+    \resizebox{\textwidth}{!} {
+    \begin{tabular}{ l | l |}
+      {\bf Dependent Variable} & {\bf R-squared Value}\\
+    \hline
+    Wait Time& 0.1642 \\
+    \hline
+    Call Time& 0.0569\\
+    \hline
+    Goal Met& 0.2458\\
+    \hline
+    Interaction Value& 0.234\\
+    \end{tabular}
+    }
+    \end{table}
+R-squared values range from 0 to 1. A R-squared value of 1 means that all movements of a variable are completely explained by another variable. 
+Overall, the higher the R-squared the better.
 \section*{Discussion}
+Overall, the best agent model would be the model with the highest R-squared value and Pearson Coefficient. In this case, this would be
+AvgGoalMet= 0.986 - 0.216*CallsPerAgent. A close second place would be AvgWaittime= -5.292 + 61.148*CallsPerAgent, as it had a decent 
+Pearson coefficient and R-squared value. Unfortunately, because of the Pearsons Coefficient I would not recommend the Interaction Value model however even though it had a good 
+r-squared value. Overall the other 3 models are would suggest to an individual to use to determine how many agents
+there business to have. Unfortunately, there are so many aspects to just this. In regards to a business perspective, the call center must have
+a budget so it is a difficult road to navigate. But, I believe it is possible to find a balance in between to ultimately maximize efficiency.
+We were also able to forecast call center volume using historical data and the ratio of how many hours the call center is open compared to each day to
+a week.
+
+  The biggest limitation I would say was that there is no right answer to answering the calls per agent problem. In an ideal situation, you would have
+plenty of agents so waittime is completely reduced. However that is not efficient or plausible. I also do wish I knew the answer to what
+the actual Goal time was, this would help me be more confident in my model I created. I did try to create a model to the ratio of Calls Per Agent,
+but Unfortunately the parameters estimates were simply just inaccurate.
+
+Another challenge was dealing with the time complexities in the dataset. There are 6 days of the week, 47 15-minute-intervals across any day, which each occur a different number of times,
+and 213 15-minute-intervals across each week. This does not average out between days of the week. There was also 139 weeks in the data, 971 days in all the data, and
+27377 15-minute-intervals in all the data. So this fails to account for discrepancies in between days of the week. Also, Call time and any values
+about the all are data explicitly about the call so they are in the row in the itself, so we have to normalize the number of agents by number of calls During
+that period recorded before we run a model comparing both values. So overall, there was a lot of data cleaning and preparing needed in this dataset, that
+took time away from the data analysis.
+
+  I still believe this study can be expanded on.
+Monday has a wait time of 175 seconds while Friday has a wait time of 88.2 seconds.
+Possibly multivariate regression technqiues could be used to model the number of agents needed.
+With the data at my hands, I could also try to answer questions such as if call length is dependenton call reason or even do an analysis on if all agents are performing
+on the same level. In detail, \citep{evensen1999effective} believes that "Since the primary interface between a financial institution and its customer is a service
+representative, this element strongly influences an institution's ability to deliver quality service.An organization’s human resource (HR) practices effect how well its employees are able to perform.
+More
+specifically, human resource practices directly influence how knowledgeable an employee is about the product offering, whether or not an employee is empowered to resolve customer issues in real time, and the
+level of turnover within the organization".
+This is an interesting point as one could analyze how Human Resources Data plays a role in qualities like AgentHandleTime that reflects on the agents performance.
+Another interesting question to look into was the abandonment
+rate and if how many times someone will call back the same day.
+I personally did not look into the chat feature that much, but I am sure that there is some interesting information like if people tend to reuse often.
+Another topic of interest is how does call center volume change on when there is an information technology problem such as the online banking services having an outage?
 

### 2022-11-14 References/Manuscript.tex
commit #update

--- 2022-11-12 Manuscript/Manuscript.tex
@@
  common to see call center volume being predicted using different techniques, but there is very limited studies on attempting to correlate
- the number of agents needed. Through Regression techniques, there are 8 models proposed to model the number of agents needed based on waittime,
+ the number of agents needed. Through Regression techniques, there are 4 models proposed to model the number of agents needed based on waittime,
  calltime, goaltime, and the amount of calls handled.
@@
 the number itself is not significant, Avramidis explains that "The maximal time a customer is willing to wait in queue is his patience time, A, also known as time-to-abandonment. The
-time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever V > W), or beginning of service (V = W).
+time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever $V  >  W$), or beginning of service (V = W).
 In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing seconds
@@
 R-squared values range from 0 to 1. A R-squared value of 1 means that all movements of a variable are completely explained by another variable. 
-Overall, the higher the R-squared the better.
+Overall, the higher the R-squared the better. The model with Goal Met as the dependent variable has the highest R-square value of 0.2458, followed by
+the model with Interaction value with an R-squared value of 0.234, then Wait time with a R-squared value of 0.1642, and lastly Call time with a R-squared value of 0.0569.
 \section*{Discussion}

### 2022-11-30 References/Manuscript.tex
commit #cleanup intro

@@
 in the United States alone, call centers play a pivotal role in a business' success. Call centers are a key part of customer service
-that will save a company time, money, and unneccessary obstacles.
-\citep{feinberg2002operational} claims call centers serve as a source of service recovery, added value, market intelligence, and strategic advantage
+that saves a company time, money, and unneccessary obstacles.
+\citep{feinberg2002operational} claims call centers serve as a source of service recovery, added value, market intelligence, and a strategic advantage.
 In the banking industry, calls can range from inquires, transfers, payments, reporting, to processing. This means members could call about their account balance, credit card bills, loan applications, 
@@
 where $B_{t}$ is the slope component, $M_{t}$ is the level component, $S_{t}$ is the seasonal component, and s is the period of seasonality.
-ARIMA models are a great model to create as "they allow the  representation of a  wide array of potentially useful predictor functions in  models  which contain relatively few parameters" \citep{newbold1983arima}.
+ARIMA models are a great model to create as "they allow for the representation of a  wide array of potentially useful predictor functions in  models  which contain relatively few parameters" \citep{newbold1983arima}.
 With the combination of Holt-Winters smoothing, Ibrahim creates a great model for forecasting call volume, however the paper never goes into detail about
-how many agents there should be working at a set time.
+how many agents that should be working at a set time.
 

### 2022-11-30 References/Manuscript.tex
commit #cleanup data

@@
 \begin{sloppypar}
-  The data comes from an undisclosed bank where I wrote two SQL queries to obtain. This comes directly from the banks records dating back from Febuary 2020
-  to Septemeber 2022, and I was lucky enough to do a data analysis on real-life data. This dataset consists of 466,565 observations of 31 variables. 
+  The data comes from an undisclosed bank where I wrote two SQL queries to obtain real life data points on their Call Center. This comes directly from the banks records dating back from Febuary 2020
+  to Septemeber 2022, in which I am lucky enough to do a data analysis on. This dataset consists of 466,565 observations of 31 variables. 
   Some significant variables consist of Calldate, Caller_ID, Caller_ID, QueuedYN, AnsweredYN, AbandonedYN, QueuedName, InteractionOutcome, 
@@
 AbandonedYN refers to if the caller ended the call before speaking to a representative. The QueuedYN is if the member was put in a queue and had to wait to speak to an agent. 
+For both AbandonedYN and QueuedYN, Y stands for Yes and N stands for No.
 The queue is an automated service or an IVR (Interactive Voice Response). The latest generation of speech-recognition technology allows
 IVRs to interpret complex user commands, so customers may be able to “self-serve”, i.e., complete the service interaction at the IVR. \citep{avramidis2005modeling}.
-Holdtime is how long the member waits when an agent places on them hold, while waittime is how long they have to wait before someone answers there call.
-WrapUpTime refers to how long the member takes to hang up the phone after the agent stops talk. AgentHandleTime is the total of Holdtime, WrapUpTime, and AgentTalkDuration combined.
+Holdtime is how long the member waits when an agent places on them hold, while Waittime is how long they have to wait before someone answers there call.
+WrapUpTime refers to how long the member takes to hang up the phone after the agent stops talking. AgentHandleTime is the total of Holdtime, WrapUpTime, and AgentTalkDuration combined.
 
-  This data is allows me to easily answer the research question as I am using real-life data. With a huge sample size and many variables,
+  This data allows me to easily answer the research question as I am using real-life data. With a huge sample size and many variables,
 this is a great opportunity for data analysis and modeling. With this dataset, I know when doing calculations such as finding means and creating plots, 
-I will able to accurately give a truly image of call center volume and agent information to a small period of time such as 15 minutes.
+I will able to accurately truly give an image of call center volume and agent information to a small period of time such as 15 minutes.
   I did do some exploratory data analysis by creating figures that represent call center volume by the year, month, day of week, and time. 
@@
 The call center consistently has a spike around 9am throughout the 3 years. This is suprising as the call center opens at 8am. This is important to be aware of when
-creating a forecasting model and having the banks employees be at their station at 9am. The decreasing trend throughout the day is not suprising
-as most people are working throughout the day. From a managers view, important to have your best employees not on break during that time so they are ready to solve 
+creating a forecasting model and having the banks employees be at their assigned station at 9am. The decreasing trend throughout the day is not suprising
+as most people are working throughout the day. From a managers point of view, it is important to have your best employees not on break during that time so they are ready to solve 
 any complications that come up. \citep{rafaeli2008impact}
@@
 Here it is prevalent that a majority of calls are handled. These variables played a key part in my models for the agents. It is also to see that 
-100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. While 
+a wait time of 100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. While 
 the number itself is not significant, Avramidis explains that "The maximal time a customer is willing to wait in queue is his patience time, A, also known as time-to-abandonment. The
 time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever $V  >  W$), or beginning of service (V = W).
-In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing seconds
-in waittime could allow for a more efficient contact call system.
+In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing a couple seconds
+in wait time could allow for a more efficient contact call system.
 \section*{Methods}

### 2022-11-30 References/Manuscript.tex
commit #methods cleanup

@@
 \end{figure}
-Here we do not see any clear pattern based on whether its winter, spring, summer, or fall. Overall, this was not too surpising.
+Here we do not see any clear pattern based on whether its winter, spring, summer, or fall. Overall, this was not too surpising as this confirms my previous findings.
 
@@
 1 if the goal was hit and 0 if it was not hit. This variable is very fluid, as each company has its own reasoning for what they want their
-goal time to be. Average Interaction Value was based off a variable that was created based on the InteractionOutcome. "Handled "got assigned 
+goal time to be. Average Interaction Value was based off a variable that was created based on the InteractionOutcome. "Handled" was assigned 
 1 as it was a positive outcome and -1 for "Abandoned" and "Leave Number" as they were deemed negative. The others were considered neutral, for example
@@
 \end{enumerate} Multicollinearity refers to the occurrence of high intercorrelations among two or more independent variables in a multiple regression model.
-To prevent this, I soley focus on one variable at a time when making my models on agents. Homoscedasticity is an assumption there is equal or similar variances in different groups being compared.
-Logistic and Linear Regression Assumptions: Violation Recognition and Control goes into detail about this stating, "it is necessary to make a note about sample size for this type of regression model.
+To prevent this, I soley focused on one variable at a time when making my models on agents. Homoscedasticity is an assumption there is equal or similar variances in different groups being compared.
+"Logistic and Linear Regression Assumptions: Violation Recognition and Control" goes into detail about this stating, "it is necessary to make a note about sample size for this type of regression model.
 In Linear
@@
 so for example, the call center gets 3.17 calls every 15 minutes on average on a Monday. It was surpising to see that Friday was the second
-lowest staffed day of the week. A possible suggestion to the company would be add an agent on Friday. Members may be calling about last minute
+lowest staffed day of the week. I would possibly suggest to the company that they should add an agent on Fridays. Members may be calling about last minute
 questions on Friday to enjoy the weekend and not have to call Saturday. In regards to Saturday, it is clear that is the least busiest day of the week,
 this is not too suprising as many people like to sleep in on the weekends and not worry about financial issues. Monday through Thursday is relatively
-consistant in all aspects. Note that the reason why the "num15minPeriods" variable is not the same is due to the outliers in the dataset where individuals
+consistant in all aspects. Note that the reason why the "Num15minPeriods" variable is not the same is due to the outliers in the dataset where individuals
 called either slightly before or after call center hours.

### 2022-11-30 References/Manuscript.tex
commit #cleanup simulation

@@
 5.25 percent of the hours. The only difference there is a different in ratio for Monday thru Thursday must be holidays, e.g. Thanksgiving. 
-The Projected Calls Per Day simply came from the total calls per week * the RatioDayPerWeek. We can also see this approach worked relatively well in the forecasting model. 
+The Projected Calls Per Day simply came from the Total calls per week * the RatioDayPerWeek. We can also see this approach worked relatively well in the forecasting model. 
 We also see that the MAPE(Mean Absolute Percent Error) is 4.21 percent. For context, a MAPE score less than 5 is very accurate.
@@
 
-  From there I ran Correlation between CallsPerAgent and the dependent variables.
+  From there I ran Correlations between CallsPerAgent and the dependent variables.
 The Pearson Product Moment Correlation test can take a range of values from 1 to -1.
@@
 variable decreases so does the independent variable.
-The stronger the correlation between the variables the higher it is to 1 or -1.
+The stronger the correlation between the variables the closer it is to 1 or -1.
 The 4 dependent variables were Average Wait Time, Average Call Time, Average Goal Being Met, Average Interaction Value.
@@
 Call Time. Goal Time and Calls Per Agents have the strongest relationship, in this case a negative medium relationship, which states as
-Calls Per Agents increases, the Goal Being Met decreases. This means the Average Goal Time is nothing being hit consistently when Calls 
+Calls Per Agents increases, the Goal Being Met decreases. This means the Average Goal Time is not being hit consistently when Calls 
 are increasing. Interaction Value and Calls Per Agent have a medium positive relationship. However, in theory, as calls increase there should

### 2022-11-30 Manuscript/Manuscript.tex
commit #update
commit #final cleanup

@@
 Here it is prevalent that a majority of calls are handled. These variables played a key part in my models for the agents. It is also to see that 
-100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. While 
+a wait time of 100 seconds is the cutoff for most people that Abandoned. That could be a goal for this bank to get too, to prevent more Abandoned calls. While 
 the number itself is not significant, Avramidis explains that "The maximal time a customer is willing to wait in queue is his patience time, A, also known as time-to-abandonment. The
-time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever V > W), or beginning of service (V = W).
-In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing seconds
-in waittime could allow for a more efficient contact call system.
+time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever $V  >  W$), or beginning of service (V = W).
+In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing a couple seconds
+in wait time could allow for a more efficient contact call system.
 \section*{Methods}
@@
 Pearson coefficient and R-squared value. Unfortunately, because of the Pearsons Coefficient I would not recommend the Interaction Value model however even though it had a good 
-r-squared value. Overall the other 3 models are would suggest to an individual to use to determine how many agents
-there business to have. Unfortunately, there are so many aspects to just this. In regards to a business perspective, the call center must have
-a budget so it is a difficult road to navigate. But, I believe it is possible to find a balance in between to ultimately maximize efficiency.
-We were also able to forecast call center volume using historical data and the ratio of how many hours the call center is open compared to each day to
-a week.
+r-squared value. Overall the other 3 models have a better Pearsons Coefficient and are more useful to an individual to use to determine how many agents
+their business to have. Unfortunately, there are so many aspects to staffing a call center. In regards to a business perspective, the call center must have
+a budget so it is a difficult road to navigate. But, I believe it is possible to find a balance between budgeting and acheiveing maximize efficiency.
+I was also able to forecast call center volume using historical data and the ratio of how many hours the call center is open compared to each day to
+a week which is important for managers to know when they designate breaks to their employees.
 
@@
 27377 15-minute-intervals in all the data. So this fails to account for discrepancies in between days of the week. Also, Call time and any values
-about the all are data explicitly about the call so they are in the row in the itself, so we have to normalize the number of agents by number of calls During
-that period recorded before we run a model comparing both values. So overall, there was a lot of data cleaning and preparing needed in this dataset, that
+about the all are data explicitly about the call so they are in the row in the itself, so we have to normalize the number of agents by number of calls during
+that period recorded before I ran a model comparing both values. So overall, there was a lot of data cleaning and preparing needed in this dataset, that
 took time away from the data analysis.
@@
 on the same level. In detail, \citep{evensen1999effective} believes that "Since the primary interface between a financial institution and its customer is a service
-representative, this element strongly influences an institution's ability to deliver quality service.An organization’s human resource (HR) practices effect how well its employees are able to perform.
+representative, this element strongly influences an institution's ability to deliver quality service.
+An organization’s human resource (HR) practices effect how well its employees are able to perform.
 More
-specifically, human resource practices directly influence how knowledgeable an employee is about the product offering, whether or not an employee is empowered to resolve customer issues in real time, and the
+specifically, human resources practices directly influence how knowledgeable an employee is about the product offering, whether or not an employee is empowered to resolve customer issues in real time, and the
 level of turnover within the organization".
